Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Add interview results & reorder results

\section{Material}
Before creating the prototype, we were free in choosing \emph{how} we were going to implement the emotion
recognition. However, there were a couple restrictions and requirements. First, a very limited time span
to create the prototype in. The prototype had to be up and running in roughly 8 weeks so that we could
use it to perform our research. Secondly, preferable everything about the prototype had to be open source, as
requested by the Waag Society. Because of prior desk-research, combined with the above restrictions, we
chose to use facial expression recognition using a camera as the basis for our prototype. This decision was
further solidified upon the discovery of several articles regarding open source facial expression software
using Python, OpenCV, Dlib, and Facial Landmarks \cite{gent2016landmarks}.

@@

\subsection{Test results}
We present a table with the results of the interview. The table gives an overview of the answers given by the
participants regarding the accuracy of the prototype. Furthermore, several line charts are given which show
the average emotions of all participants from each video, and the expected emotions as a dashed vertical line.

@@

@@

Our first question was: \emph{Do the participants agree with the emotions predicted by the prototype?}.
Out of the 13 research participants, X agreed that the emotions depicted by the prototype, were correct with
how they felt. Therefore, we can conclude that yes, the participants mostly agreed with the results from the
prototype. One emotion often stood out as possibly wrong, namely \emph{disgust}. Many people also agreed,
however, that this might be because of they way they look normally. This could mean that either people often
look with disgust by default, or that neutral and disgust were not properly distinguished from each other by
the prototype. This could be solved by either letting the participants review the video of themselves to see
if they agree with the judgment of the prototype, or by improving the dataset used to train the SVM model,
thereby increasing the accuracy.

@@

If we combine the positive answers for both of the above questions, we get a fairly clear image of the accuracy
and usability of the prototype. Although further improvements are necessary, for example a larger dataset,
the prototype works sufficiently well to be used in starting a discussion. Out of 13 participants, X agreed that
the visualization, especially in group settings, is capable of helping in starting a discussion regarding their
emotions on a specific subject.

>>>>

\section{Material}
Before creating the prototype, we were free in choosing \emph{how} we were going to implement the emotion
recognition. However, there were a couple restrictions and requirements. First, a very limited time span
to create the prototype in. The prototype had to be up and running in roughly 8 weeks so that we could
use it to perform our research. Secondly, preferable everything about the prototype had to be open source, as
requested by the Waag Society. Because of prior desk-research, combined with the above requirements, we
chose to use facial expression recognition using a camera as the basis for our prototype. This decision was
further solidified upon the discovery of several articles regarding open source facial expression software
using Python, OpenCV, Dlib, and Facial Landmarks \cite{gent2016landmarks}.

@@

\subsection{Test results}
We present an overview of the interview results, including demographic, as well as opinions regarding the
prototype. Furthermore, several line charts are given which show
the average emotions of all participants from each video, and the expected emotions as a dashed vertical line.

@@

\subsection{Interview results}
The interview contained several questions consisting questions about the background of the participant and
questions about the experience regarding the prototype.

The total number of participants was 13. The genders of the participants contained 11 men and 2 women.
The participants differed in age, 9 participants were aged between 20-23, 3 participants between 24-27 and 1
of the participants was aged 28-30. Only one of the participants was an only child, all the other participants
had a family composition which contained one or more brothers or one or more sisters. 9 out of 13
participants didn't have a religious conviction, 2 are Atheists, 1 is Islam and the last one doesn't believe
in anything. 11 out of 13 of the participants live in Noord-Holland, the two other provinces are Flevoland and
Zuid-Holland. Also 11 out of 13 participants live in a city, the two others live in a village. 7 out of 13
participants live with their parents, 5 live on their own and 1 participant lives together with their partner.
8 out of the 13 participants are in a relationship, 4 are single and 1 participant is engaged.
Of the respondents, 11 out of 13 follow a higher professional education, the other two study at university level.
The disciplines consist largely (10/13) of ‘Exact and Informatics’ in addition to ‘Behavior and Society’,
‘Education and Upbringing’ and ‘Law and Administration’. 10 participants are in the last (fourth) year of their
education, two of them are in their third year and one of them in the second year of their education.
12 out of 13 participants have a job besides their study. 8 people did come in contact with foreign religions.

The questions from the interview have validated that 12 of the 13 participants found the visualized model clear
and understood what the model showed. Of these participants 11 of the 13 indicated that the emotions that the
model showed corresponded to the emotions that they felt during the video. 8 Participants indicated that they
showed the emotion happy, in all of these cases the visualized model corresponded with this emotion.
With the emotion ‘disgust’ there is 1 person who has indicated to have actually experienced this emotion,
yet the model showed differently and 6 of the 13 people showed the emotion disgust at some point or time frame
in the video.

The interview showed that everyone partially understood the visualized model, but that they did not immediately
see that the model showed the emotions over time. On the other hand, all participants were enthusiastic about
the overall visualized model after they had been given an explanation of how the visualized model worked
exactly. 12 of the 13 participants also found it interesting to see their own emotions; in addition,
the same 12 people felt that the prototype can certainly contribute to stimulating a discussion.
The participants indicated there must be a certain form of intelligence or an age, older people will not be
able to fully understand this prototype and thus ultimately not achieve the goal.

@@

Our first question was: \emph{Do the participants agree with the emotions predicted by the prototype?}.
Out of the 13 research participants, 12 agreed that the emotions depicted by the prototype, were correct with
how they felt. Therefore, we can conclude that yes, the participants mostly agreed with the results from the
prototype. One emotion often stood out as possibly wrong, namely \emph{disgust}. Many people also agreed,
however, that this might be because of they way they look normally. This could mean that either people often
look with disgust by default, or that neutral and disgust were not properly distinguished from each other by
the prototype. This could be solved by either letting the participants review the video of themselves to see
if they agree with the judgment of the prototype, or by improving the dataset used to train the SVM model,
thereby increasing the accuracy.

@@

If we combine the positive answers for both of the above questions, we get a fairly clear image of the accuracy
and usability of the prototype. Although further improvements are necessary, for example a larger dataset,
the prototype works sufficiently well to be used in starting a discussion. Out of 13 participants, 12 agreed that
the visualization, especially in group settings, is capable of helping in starting a discussion regarding their
emotions on a specific subject.
